\begin{thebibliography}{00}

    \bibitem{Mountcastle}
    V. B. Mountcastle.
    ``The Columnar Organization of the Neocortex.''
    \textit{Brain: A Journal of Neurology}
    (1997).

    \bibitem{Hawkins}
    J. Hawkins, R. Dawkins.
    ``A Thousand Brains: A New Theory of Intelligence.''
    \textit{Basic Books}
    (2021).

    \bibitem{Structure-Functional}
    E. Bullmore, O. Sporns.
    ``Complex Brain Networks: Graph Theoretical Analysis of Structural and Functional Systems.''
    \textit{Nature Reviews Neuroscience}
    (2009).

    \bibitem{TNN}
    H. Nair, J. P. Shen, J. E. Smith.
    ``A Microarchitecture Implementation Framework for Online Learning with Temporal Neural Networks.''
    \textit{IEEE Computer Society Annual Symposium on VLSI (ISVLSI)}
    (2021).

    \bibitem{Macrocolumn}
    J. E. Smith.
    ``A Macrocolumn Implemented with Spiking Neurons.''
    \textit{arXiv preprint arXiv:2207.05081}
    (2023).

    \bibitem{Encoding}
    S. Purdy.
    ``Encoding Data for HTM Systems.''
    \textit{arXiv preprint arXiv:1602.05925}
    (2016).

    \bibitem{LSM}
    W. Maass.
    ``Liquid State Machines: Motivation, Theory, and Applications.''
    \textit{Computability in Context: Computation and Logic in the Real World}
    (2011).

    \bibitem{Kohonen}
    T. Kohonen.
    ``Self-Organized Formation of Topologically Correct Feature Maps.''
    \textit{Biological Cybernetics}
    (1982).

    \bibitem{LSM Constraints}
    H. Hazan, L. M. Manevitz.
    ``Topological Constraints and Robustness in Liquid State Machines.''
    \textit{Expert Systems with Applications}
    (2012).

    \bibitem{Hodgkin-Huxley}
    A. L. Hodgkin, A. F. Huxley.
    ``Currents Carried by Sodium and Potassium Ions Through the Membrane of the Giant Axon of Loligo.''
    \textit{The Journal of Physiology}
    (1952).

    \bibitem{STDP}
    M. M. Taylor.
    ``The Problem of Stimulus Structure in the Behavioural Theory of Perception.''
    \textit{The South African Journal of Psychology}
    (1973).

    \bibitem{Astrocyte}
    V. Ivanov, K. Michmizos.
    ``Increasing Liquid State Machine Performance with Edge-of-Chaos Dynamics Organized by Astrocyte-modulated Plasticity.''
    \textit{Advances in Neural Information Processing Systems (NeurIPS)}
    (2021).

    \bibitem{MNIST Dataset}
    AstroDave, W. Cukierski.
    ``Digit Recognizer.''
    \textit{Kaggle}
    (2012).
    \url{www.kaggle.com/competitions/digit-recognizer}

    \bibitem{Kheradpisheh}
    S. R. Kheradpisheh, M. Ganjtabesh, S. J. Thorpe, T. Masquelier.
    ``STDP-Based Spiking Deep Convolutional Neural Networks for Object Recognition.''
    \textit{arXiv preprint arXiv:1611.01421}
    (2016).

\end{thebibliography}